---
title: "Codebook"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    code_folding: 'hide'
    self_contained: true
  pdf_document:
    toc: yes
    toc_depth: 4
    latex_engine: xelatex
---

The `codebook` package will automatically format metadata, summary statistics, missing tables, and a codebook based on your data. The following code generates a full codebook using your data. This includes summary statistics for each variable, a missing report, and the codebook. To create codebook, run `codebook::new_codebook_rmd()` in your console, which will load a new R markdown file with preset defaults. 

An overview of the package can be found at: https://rubenarslan.github.io/codebook/index.html. A helpful tutorial on creating and updating the codebook can be found here:  https://rubenarslan.github.io/codebook/articles/codebook_tutorial.html. 

```{r , include = FALSE}
knitr::opts_chunk$set(echo = TRUE)

ggplot2::theme_set(ggplot2::theme_bw()) # preset theme from codebook

# load dependencies
library(codebook) # load the codebook package
library(labelled) # load to update label names
```

```{r run_codebook, include = TRUE}
library(ID529data) # load data 

data(nhanes_id529, package = 'ID529data')

#codebook(nhanes_id529) # generates codebook and summary statistics for each variable
compact_codebook(nhanes_id529) # generates the codebook only
```

